---
title: "First R Markdown"
author: "Vinicius Padovani"
date: "15/01/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown Test edit

## Cheat Sheet Guide

Built with
`r getRversion()`

```{r echo=TRUE}
getRversion()
```

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


New paragraph  
`code`  
sub^{~4~}  
sup^{4}  
~~strike~~  
esc \* \_ \\  
en --  
em ---  
$A = \pi*r^{2}$  
$$E = mc^{2}$$  
> quote  
blablabla  

# Header 1 {#anchor}  
### Header 2 {#css_id}  
### Header3 {.css_class}  


<!--comment-->  

\ texbf{Tex ignored in HTML}  
<em>HTML ignored in pdfs<em>  

<http://www.youtube.com>  

[link](http://www.youtube.com)  

jump to [Header 1](#anchor)

![caption] (image)

- bullet list 1     
>- bulet 2   

*Unordered list
    + sub-item 1
        - sub-sub-item 1
        

1. ordered list
    i) sub_1
        I. sub_sub_1
        

(@) Continuous list
(@) keeps going  

:   Defitinition  

|TABLE 1|BLABLA|
|------:|:----:|
|VALUE 1|VALUE 2|

Footnote [^1]

[^1]: Footnote




```{r cars}
summary(cars)
```

## Including Plots

```{r pressure, echo=FALSE}
plot(pressure)
```

Horizontal rule:
***